%Section: Work Experience
\sectionTitle{Professional Experience}{\faSuitcase}

\begin{experiences}

\consultantexperience
    {July 2024} {Senior Consultant}{\link{https://www.dbi-services.com/fr/expertises/digitalisation-avec-ecm/}{DBI Services}}{Basel, Switzerland}
    {April 2017}    {Consultant}{Novartis, Bank for International Settlements, Johnson \& Johnson, United Nations, ...} {
        \begin{itemize}[left=0pt,label={},itemsep=0.5em]

          \item \textbf{ECM Administration \& Integration}:
            \begin{itemize}[itemsep=0.2em,topsep=0.2em,parsep=0pt]
              \small
              \item Installed, updated, and migrated \textbf{Documentum} platforms (Content Server, Rendition Server, Application Server, Full Text Server) in multi-node environments.
              \item Deployed and integrated \textbf{Adobe Experience Manager (AEM)} clusters with Documentum.
              \item Managed patches and upgrades in regulated \textbf{GxP} environments.
            \end{itemize}

          \item \textbf{Consulting \& Security}:
            \begin{itemize}[itemsep=0.2em,topsep=0.2em,parsep=0pt]
              \small
              \item Conducted feasibility studies, architecture, and security reviews.
              \item Integrated with \textbf{Active Directory} and implemented \textbf{SSO (SAML2, OpenID)} solutions.
            \end{itemize}

          \item \textbf{High Availability \& Business Continuity}:
            \begin{itemize}[itemsep=0.2em,topsep=0.2em,parsep=0pt]
              \small
              \item Designed \textbf{HA/DR/OR} architectures, backup strategies, and disaster recovery tests.
              \item Migrated documents and applications across heterogeneous environments.
            \end{itemize}

          \item \textbf{DevOps \& Automation}:
            \begin{itemize}[itemsep=0.2em,topsep=0.2em,parsep=0pt]
              \small
              \item Automated Documentum/AEM deployments using \textbf{Kubernetes} and \textbf{Ansible}.
              \item Set up and managed \textbf{Kubernetes clusters} integrated with \textbf{CI/CD pipelines}.
              \item Migrated Documentum environments from VMs to Kubernetes (containers \& microservices).
              \item Conducted performance and load testing.
            \end{itemize}

          \item \textbf{Kubernetes, Monitoring \& Cloud}:
            \begin{itemize}[itemsep=0.2em,topsep=0.2em,parsep=0pt]
              \small
              \item Designed, implemented, and maintained large-scale \textbf{Kubernetes clusters}.
              \item Implemented infrastructure and application \textbf{monitoring} with Prometheus, Grafana, and ELK Stack.
              \item Delivered \textbf{training workshops} on Prometheus and Grafana in French and English.
              \item Prepared \textbf{Azure labs} using Terraform.
            \end{itemize}

          \item \textbf{Leadership \& Coaching}:
            \begin{itemize}[itemsep=0.2em,topsep=0.2em,parsep=0pt]
              \small
              \item Supervised and coached offshore support teams.
              \item Contributed to DevOps best practices and knowledge transfer.
            \end{itemize}

        \end{itemize}
    }
    {OpenText Documentum, Adobe Experience Manager, WebLogic Server, JBoss/WildFly, Apache Tomcat, Kubernetes, Docker, Jenkins, Jira, GitLab CI/CD, Helm, Kustomize, Ansible, Prometheus, Grafana, ELK Stack, Nginx, Terraform, Azure}

\emptySeparator
\emptySeparator

\consultantexperience
    {March 2017}       {Production Engineer}{AtoS}{France}
    {January 2011}    {Consultant Engineer}{PriceWaterhouseCoopers, GDF Suez, Givaudan, BNP Cardif, AtoS, Veolia} {
        \begin{itemize}[left=0pt,label={},itemsep=0.4em]

          \item \textbf{ECM Administration \& Infrastructure}:
            \begin{itemize}[itemsep=0.15em,topsep=0.1em,parsep=0pt]
              \small
              \item Administered and migrated \textbf{SharePoint} farms (2010–2013) and other ECM platforms (\textbf{Documentum, OpenText}) in multi-server environments.
              \item Managed applications and server infrastructure (\textbf{SQL Server, WebSphere, Apache Tomcat, Prophet Enterprise}).
              \item Deployed custom solutions, monitored performance, managed incidents, and applied updates.
            \end{itemize}

          \item \textbf{Migration \& Business Continuity}:
            \begin{itemize}[itemsep=0.15em,topsep=0.1em,parsep=0pt]
              \small
              \item Participated in migrations (CRM, SQL, custom applications) and supported disaster recovery (DRP) planning.
            \end{itemize}

          \item \textbf{Coordination \& Offshore Management}:
            \begin{itemize}[itemsep=0.15em,topsep=0.1em,parsep=0pt]
              \small
              \item Coordinated with offshore teams (Poland, Morocco, India) and managed documentation processes.
            \end{itemize}

        \end{itemize}
    }
    {SharePoint 2010/2013, Documentum, OpenText, SAP, Oracle, SQL Server, DB2, WebSphere, Apache Tomcat, WebSphere Integration Developer, Veritas Cluster, CFT, ControlM, Prophet Enterprise, Prophet Professional, TWS, VTom, VMware, NetBackup, PowerShell, Bash, Hyper-V}

\emptySeparator

\consultantexperience
    {December 2010} {Applications Technical Lead}{\link{https://atos.net/}{AtoS}}{France}
    {October 2003}    {Consultant}{Solvay, Bluestar Silicones, Sephora} {
        \begin{itemize}[left=0pt,label={},itemsep=0.5em]

          \item \textbf{Backup \& Scheduling}:
            \begin{itemize}[itemsep=0.2em,topsep=0.2em,parsep=0pt]
              \small
              \item Administered backup and scheduling systems (\textbf{NetBackup, Dollar Universe, Automator}).
              \item Installed and configured tape libraries (\textbf{HPE ESL L700, SL500, HPESL322e}) in datacenters.
              \item Performed daily maintenance, functionality checks, and equipment monitoring.
              \item Conducted quarterly audits of tape libraries to ensure compliance, availability, and data security.
            \end{itemize}

          \item \textbf{ERP \& Applications}:
            \begin{itemize}[itemsep=0.2em,topsep=0.2em,parsep=0pt]
              \small
              \item Managed ERP and non-ERP applications (\textbf{SAP, Oracle, Documentum}) and deployed custom solutions.
              \item Trained offshore teams (Morocco, India) and managed incidents and change requests.
            \end{itemize}

          \item \textbf{Documentation \& Risk Management}:
            \begin{itemize}[itemsep=0.2em,topsep=0.2em,parsep=0pt]
              \small
              \item Authored technical documentation and implemented risk management procedures.
            \end{itemize}

        \end{itemize}
    }
    {SAP, Oracle, SQL, Automator, Dollar Universe, Sentinel, CFT, Backup Exec, NetBackup, VMware, ESX, BCV, EMC Snapshot, VCB, Enabler Solution, Nagios, Dyamon, UniqPrint, CRM360, WebSphere, Application Server}

\emptySeparator
\end{experiences}
